LayeredTypes -- Independently combine type systems

### 2023-03-10 paper/types2023.tex
Added references to types submission

\begin{document}

\maketitle

@@

We want to note an important distinction to Gradual Typing\cite{gradual}: While the latter is concerned with only providing partial typing information and making it gradually more precise, our approach does not focus on the information provided to the verifier, but rather on \textit{how} this information.

@@

%------------------------------------------------------------------------------

>>>>

\begin{document}
\maketitle

@@

We want to note an important distinction to Gradual Typing\cite{gradual}\cite{gradual-objects}: While the latter is concerned with only providing partial typing information and making it gradually more precise, our approach does not focus on the information provided to the verifier, but rather on \textit{how} this information.

@@

%------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{literature}
